Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-07 talk/icooolps2011/paper.tex
I think Python object model contains more hard features, but those are the major ones
add a note

To implement this object model, we could use the RPython code in
Figure~\ref{fig:interpreter-slow} as part of the interpreter source code.
In this straightforward implementation the methods and attributes are just
stored in dictionaries (hash maps) on the classes and instances, respectively.
While this object model is very
simple it already contains all the hard parts of Python's object model. Both
instances and classes can have arbitrary fields, and they are changeable at
any time.  Moreover, instances can change their class after they have been
created.

@@

>>>>

To implement this object model, we could use the RPython code in
Figure~\ref{fig:interpreter-slow} as part of the interpreter source code.
In this straightforward implementation the methods and attributes are just
stored in dictionaries (hash maps) on the classes and instances, respectively.
While this object model is very
simple it already contains most hard parts of Python's object model. Both
instances and classes can have arbitrary fields, and they are changeable at
any time.  Moreover, instances can change their class after they have been
created.

@@

XXX [fijal] maybe it's worth noting that those guards are removed out of
    the loop by loop-invariant-code motion, unless our is so special
    we want to write a special paper about it
